### 2012-02-02 sermons/Revelation1:1-3.tex
Updated sermon.

\subsubsection{He is King}
\subsection{Who is it from?}
\subsection{What is its purpose?}
\subsection{Who is it to?}
\subsection{What is its focus?}

>>>>

\subsubsection{He is the conquering King}
\I Rev 1:7 \Q{Behold, He is coming with clouds, and every eye will see Him, 
                even they who pierced Him. And all the tribes of the earth
                will mourn because of Him. Even so, Amen.}
\I Rev 1:14-16 \Q{His head and hair were white like wool, as white as snow,
                and His eyes like a flame of fire; His feet were like brass, 
                as if refined in a furnace, and His voice as the sound of 
                many waters; He had in his right hand seven stars, 
                out of His mouth went a sharp two-edged sword, 
                and His countenance was like the sun shining in its strength.}
\I Rev 6:16-17 \Q{\ldots and said to the mountains and rocks, 
                ``Fall on us and hide us from the face of Him who sits on the
                throne and from the wrath of the Lamb! For the great day of His
                wrath has come, and who is able to stand?''}
\I Rev 14:14 \Q{Then I looked, and behold, a white cloud, and on the cloud
                sat One like the Son of Man, having on His head a golden crown, 
                and in His hand a sharp sickle.}
\I Rev 17:14 \Q{``These [ten kings and the beast] will make war with the Lamb, 
                and the Lamb will overcome them, for He is Lord of lords and
                King of kings; and those who are with Him are called, 
                chosen, and faithful.''}
\I Rev 19:11-16 \Q{Now I saw heaven opened, and behold, a white horse.
                And He who sat on Him was called Faithful and True,
                and in righteousness He judges and makes war.
                His eyes were like a flame of fire, and on His head were
                many crowns. He had a name written that no one knew except
                Himself. He was clothed with a robe dipped with blood,
                and His name is called The Word of God.
                And the armies of heaven, clothed in fine linen, white and
                clean, followed Him on white horses.
                Now out of His mouth goes a sharp sword, that with it He 
                should strike the nations. And He Himself will rule them 
                with a rod of iron. He Himself treads the winepress of the
                fierceness and wrath of Almighty God. And He has on His robe 
                and on His thigh a name written:
                \Q{KING OF KINGS \\ AND LORD OF LORDS.}}

\I Rev 20:15 \Q{And anyone not found written in the Book of Life was cast 
                into the lake of fire.}
            Note: we know this is the Lamb's Book of Life from Rev 13:8.

\subsection{Who is it from?}
\subsection{What is its purpose?}
\subsection{Who is it to?}
\subsection{What is its focus?}
